### 2018-07-05 paper/6-engineering.tex
Polish S6.7-S7

Our build system abstraction assumes a \hs{k}/\hs{v} store, along with a build
system that works directly on \hs{k} and \hs{v} values. However, certain build
systems provide greater flexibility, e.g. \Shake permits polymorphic keys and
values, allowing types that are only stored in the \Shake information, and never
persisted to the store.

As one example of richer key/value types, consider the version of
\cmd{gcc}~--~for many builds it should be a dependency. In \Shake it is possible
to define an \emph{oracle} rule as per~\cite{mitchell2012shake} whose value is
the result of running \cmd{gcc --version} and which is volatile, making the
\cmd{gcc} version something that can be depended upon. Of course, provided the
build can express volatile dependencies and supports cutoff, the version number
could equally be written to a file and used in a similar way.

>>>>

Our build system abstraction assumes a \hs{k}/\hs{v} store, along with a build
system that works directly on \hs{k} and \hs{v} values. However, some build
systems provide greater flexibility, e.g. \Shake permits polymorphic keys and
values, allowing types that are stored only in the \Shake's build information.

As one example of richer key/value types, consider the version of
\cmd{gcc}~--~for many builds it should be a dependency. In \Shake it is possible
to define an \emph{oracle} rule as per~\cite{mitchell2012shake} whose value is
the result of running \cmd{gcc -}\cmd{-version} and which is volatile, making the
\cmd{gcc} version something that can be depended upon. Of course, provided the
build can express volatile dependencies and supports cutoff, the version number
could equally be written to a file and used in a similar way.

### 2018-07-05 paper/7-related.tex
Polish S6.7-S7

Most build systems, when viewed at the level we talk, can be captured with minor
variations on the code presented in \S\ref{sec-implementations}. As some
examples:

\begin{itemize}
\item \Ninja~\cite{ninja} combines the \hs{topological} scheduler of \Make with
the verifying traces of \Shake~--~our associated implementation provides such a
combination. \Ninja~is also capable of modelling build rules that produce
multiple results, a limited form of polymorphism \S\ref{sec-polymorphism}.

\item \Tup~\cite{tup} functions much like \Make, but with a refined dirty-bit
implementation that watches the file system for changes and can thus avoid
rechecking the entire graph, and with automatic deleting of stale results.

@@

\item \Dune~\cite{dune} is a build system designed for OCaml/Reason projects.
Its distinguishing feature is that it uses
\emph{arrows}~\cite{hughes2000generalising} rather than monads to model
dynamic dependencies, which simplifies static dependency approximation.
\end{itemize}

@@

\begin{minted}[xleftmargin=10pt]{haskell}
data Key = A Integer | B Integer | D Integer Integer deriving Ord
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
editDistance :: Tasks Monad Key Integer
editDistance (D i 0) = Just $ Task $ const $ pure i
editDistance (D 0 j) = Just $ Task $ const $ pure j
editDistance (D i j) = Just $ Task $ \fetch -> do
    ai <- fetch (A i)
    bj <- fetch (B j)
    if ai == bj then fetch (D (i - 1) (j - 1))
                else do insert  <- fetch (D  i      (j - 1))
                        delete  <- fetch (D (i - 1)  j     )
                        replace <- fetch (D (i - 1) (j - 1))
                        return (1 + minimum [insert, delete, replace])
editDistance _ = Nothing
\end{minted}

>>>>

Most build systems, when viewed at the level we talk, can be captured with minor
variations on the code presented in \S\ref{sec-implementations}. Below we list
some notable examples:

\begin{itemize}
\item \Dune~\cite{dune} is a build system designed for OCaml/Reason projects.
Its distinguishing feature is that it uses
\emph{arrows}~\cite{hughes2000generalising} rather than monads to model
dynamic dependencies, which simplifies static dependency approximation.

\item \Ninja~\cite{ninja} combines the \hs{topological} scheduler of \Make with
the verifying traces of \Shake~--~our associated implementation provides such a
combination. \Ninja~is also capable of modelling build rules that produce
multiple results, a limited form of polymorphism \S\ref{sec-polymorphism}.

@@

\item \Tup~\cite{tup} functions much like \Make, but with a refined dirty-bit
implementation that watches the file system for changes and can thus avoid
rechecking the entire graph, and with automatic deleting of stale results.
\end{itemize}

@@

\begin{minted}[xleftmargin=10pt, fontsize=\small]{haskell}
data Key = A Integer | B Integer | D Integer Integer
\end{minted}
\vspace{0mm}
\begin{minted}[xleftmargin=10pt, fontsize=\small]{haskell}
editDistance :: Tasks Monad Key Integer
editDistance (D i 0) = Just $ Task $ const $ pure i
editDistance (D 0 j) = Just $ Task $ const $ pure j
editDistance (D i j) = Just $ Task $ \fetch -> do
    ai <- fetch (A i)
    bj <- fetch (B j)
    if ai == bj then fetch (D (i - 1) (j - 1))
                else do insert  <- fetch (D  i      (j - 1))
                        delete  <- fetch (D (i - 1)  j     )
                        replace <- fetch (D (i - 1) (j - 1))
                        return (1 + minimum [insert, delete, replace])
editDistance _ = Nothing
\end{minted}
